Applications of technology and large data in statistics education and statistical graphics

### 2015-07-12 Appendix/Appendix1.Rnw
formatting edits

<<ARTISTModDiag, echo=FALSE , warning=FALSE, fig.width=5, fig.height=5, out.width='.49\\linewidth', fig.pos='h',fig.align='center',fig.cap="Normal quantile plots (left) and bivariate scatterplot (right) for residuals of each response from ARTIST Model.",fig.show='hold'>>=
#--------------------------------------------------
### Check Conditions for MANCOVA linear model fit
## check response correlations to avoid colinearity in multivariate model
#Rule of Thumb: ~ .3 to .55 then MANCOVA will work well
#with(dat, cor(ConfMC,HypMC)) #Not overly correlated

@@

<<AppliedModDiag, echo=FALSE , warning=FALSE, fig.width=5, fig.height=5, out.width='.49\\linewidth', fig.pos='h',fig.align='center',fig.cap="Normal quantile plots (left) and bivariate scatterplot (right) for residuals of each response from Applied Model.",fig.show='hold'>>=
#--------------------------------------------------
### Check Conditions for MANCOVA linear model fit
## check response correlations to avoid colinearity in multivariate model
#Rule of Thumb: ~ .3 to .55 then MANCOVA will work well
#with(dat, cor(AppliedCI,AppliedHT)) #Not overly correlated

>>>>

<<ARTISTModDiag, echo=FALSE , warning=FALSE, fig.width=5, fig.height=5, out.width='.49\\linewidth', fig.pos='h',fig.align='center',fig.cap="Normal quantile plots (left) and bivariate scatterplot (right) for residuals of each response from ARTIST Model.",fig.scap="Normal quantile plots and bivariate scatterplot for residuals of each response from ARTIST Model.",fig.show='hold'>>=
#--------------------------------------------------
### Check Conditions for MANCOVA linear model fit
## check response correlations to avoid colinearity in multivariate model
#Rule of Thumb: ~ .3 to .55 then MANCOVA will work well
#with(dat, cor(ConfMC,HypMC)) #Not overly correlated

@@

<<AppliedModDiag, echo=FALSE , warning=FALSE, fig.width=5, fig.height=5, out.width='.49\\linewidth', fig.pos='h',fig.align='center',fig.cap="Normal quantile plots (left) and bivariate scatterplot (right) for residuals of each response from Applied Model.",fig.scap="Normal quantile plots and bivariate scatterplot for residuals of each response from Applied Model.",fig.show='hold'>>=
#--------------------------------------------------
### Check Conditions for MANCOVA linear model fit
## check response correlations to avoid colinearity in multivariate model
#Rule of Thumb: ~ .3 to .55 then MANCOVA will work well
#with(dat, cor(AppliedCI,AppliedHT)) #Not overly correlated

### 2015-07-12 Preface/acknowl.tex
Finish including TISE chapter, start file structure for DB Sampler Chapter
formatting edits

Lastly, I owe an enormous debt of gratitude to my friends and family -- especially my mother and father -- for their love and support throughout my life. Thank you, I love you.

>>>>

Lastly, I owe an enormous debt of gratitude to my friends and family -- especially my mother and father, Joyce and Clayton Maurer -- for their love and support throughout my life. Thank you all.
